
\courseTemplate[
code = {INFS1200},
title = {Introduction to Information Systems},
score = {4},
prereq = {None},
contact = {3L, 1T, 1P},
coordinator = {Prof Xue Li (xueli@itee.uq.edu.au)},
assessment = {
example & example\% & example \\
},
review = {
    This course provides a comprehensive introduction to the modelling, design and implementation of a relational database system. The content is designed completely for newcomers to the field and requires no background knowledge in the area of databases or computers in general.

    The course is split into two major sections. The first section delves into the design and modelling of a database. For this, students are taught modelling techniques such as ER diagrams and data flow diagrams. In addition, students are also taught about many of the fundamental basics of databases such as the relational model and normalisation.

    The second part of the subject teaches the query language SQL and how it can be used to retrieve information from a database.

    The course also contains two assignments, the first involves creating a database schema to a given specification. The second assignment is to implement and design queries for a provided database.

    The final exam for the course is fairly easy if you have a good understanding of the theoretical basics taught at the beginning of the course. The rest of the course is all derived from this knowledge and understanding that will make the final exam much easier to tackle.

    Attendance for the course is not mandatory, however it is recommended to attend classes if you are struggling with any of the course content.

    This course is strongly recommended for obtaining an understanding of database systems and as an introduction to how data is stored on a computer system. The foundational knowledge that is taught in this course is used in many other courses in nearly every computing degree.  
},
preparation = {
    \item No preparation is needed for this course as the content is designed for complete beginners to the field.
}]{}
